---
title: "My Twitter Sentiment Analysis"
author: "Brendan Dagys"
date: "6/21/2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Install the necessary packages. 'syuzhet' is for sentiment analysis. 'tm' and 'SnowballC' are used for text mining and analysis.

```{r}
# install.packages('SnowballC')
# install.packages('tm')
# install.packages('twitteR')
# install.packages('syuzhet')

library(SnowballC)
library(tm)
library(twitteR)
library(syuzhet)
```

Information obtained from the Twitter app I created, to access tweets:

```{r}
consumer_key = 'd6GKPh9ZlKV4Ykw2993HYrZij'
consumer_secret = 'UiJnzMTF2XSOObheQhtZHpm3hIcW60fkwYSysoOKew2ZlD4e4V'
access_token = '407474301-TzBGvNUmB7GejkwOr5KyzdC7eEV00ZREOQljuTK3'
access_secret = 'R81TuefVAOckYPfW3rm9tPQfmukMluuo26RY2XFbgyyHm'
```

Obtaining 94 tweets from my Twitter account:

```{r}
setup_twitter_oauth(consumer_key, consumer_secret, access_token, access_secret)
tweets = userTimeline('BrendanDagys', n = 2000)

n.tweet = length(tweets)

tweets.df = twListToDF(tweets)
```

We now will remove hashtags, mentions, and URLs from the 'text' field.

```{r}
head(tweets.df$text)

tweets.df2 = gsub('#\\w+', '', tweets.df$text)
tweets.df2 = gsub('@\\w+', '', tweets.df2)
tweets.df2 = gsub('http://[^\\s]*', '', tweets.df2)
tweets.df2 = gsub('https://[^\\s]*', '', tweets.df2)
tweets.df2
```

Now let's get the emotion score for each tweet.
The 10 emotions are: anger, anticipation, disgust, fear, joy, sadness, surprise, trust, negative, positive.

```{r}
emotion.df = get_nrc_sentiment(tweets.df2)
emotion.df2 = cbind(tweets.df2, emotion.df)
head(emotion.df2)
```

This function gives us a numeric sentiment value. Negative values are negative sentiments.
I will find the positive and most negative tweets.

```{r}
sentiment = get_sentiment(tweets.df2)

most_pos = tweets.df2[sentiment == max(sentiment)]
most_neg = tweets.df2[sentiment == min(sentiment)]

most_pos
```

This result is interesting. Although the tweet is negative in nature, the presence of the words 'good', 'win', 'favor', and 'allow'
likely triggered the sentiment function to evaluate this tweet as very positive.
It will not be correct every time due to the nature of human language...

```{r}
most_neg

positive_tweets = tweets.df2[sentiment > 0]
negative_tweets = tweets.df2[sentiment < 0]
neutral_tweets = tweets.df2[sentiment == 0]

positive_tweets
negative_tweets
neutral_tweets
```

Let's make a table of the distribution of sentiments.

```{r}
sentiment_classes = ifelse(sentiment > 0, 'Positive', ifelse(sentiment < 0, 'Negative', 'Neutral'))

table(sentiment_classes)
```

I should try to be more positive, it seems.